%% ============================================================
%% CV -- ONE PAGE
%% Allamine Mahamat Moussa
%% Compile: pdflatex -interaction=nonstopmode cv_one_page.tex
%% ============================================================
\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage[a4paper,
            top=0.7cm, bottom=0.7cm,
            left=1.5cm, right=1.5cm]{geometry}

\usepackage{xcolor}
\definecolor{navy}{RGB}{13,31,60}
\definecolor{gold}{RGB}{201,168,76}
\definecolor{mgray}{RGB}{95,105,120}

\usepackage{array}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

%% -- Tight section heading
\newcommand{\cvsection}[1]{%
  \vspace{4pt}\noindent%
  {\footnotesize\bfseries\color{navy}\MakeUppercase{#1}}%
  \par\nointerlineskip\vspace{0.5pt}%
  {\color{gold}\rule{\linewidth}{0.65pt}}%
  \par\vspace{1.5pt}%
}

%% Narrow date column; X expands to fill the line
\newcolumntype{D}{>{\raggedright\color{mgray}\footnotesize}p{2.1cm}}

%% ============================================================
\begin{document}

%% ---- HEADER -----------------------------------------------
\begin{center}
  {\large\bfseries\color{navy} Allamine Mahamat Moussa}\\[1pt]
  {\footnotesize\color{mgray}
    PhD Researcher $\cdot$ Development Economics $\cdot$
    Policy Evaluation $\cdot$ Data Analysis}\\[0.5pt]
  {\footnotesize
    Universit\'{e} Clermont Auvergne / Laboratoire d'\'Economie d'Orl\'eans (LEO)}\\[0.5pt]
  {\footnotesize\color{mgray}
    Allamine\_Mahamat.Moussa@doctorant.uca.fr \;$|$\; ORCID: 0009-0001-5953-0888
    \;$|$\; linkedin.com/in/moussa-allamine-430361178 \;$|$\; github.com/mssallamine}
\end{center}
\vspace{0.5pt}
{\color{gold}\rule{\linewidth}{0.9pt}}
\vspace{1.5pt}

%% ---- PROFILE ----------------------------------------------
\cvsection{Profile}
{\footnotesize
PhD researcher (2025--2028) at UCA/LEO. Thesis: \textit{Essays on Macroeconomic Sovereignty
in the Global South}. Research: IMF programmes, fiscal space, global financial cycles,
public investment, geospatial evaluation. Policy evaluation at ADE, Belgium (2025).
}

%% ---- EDUCATION --------------------------------------------
\cvsection{Education}
{\footnotesize
\begin{tabularx}{\linewidth}{@{} D X @{}}
2025--2028 &
  \textbf{PhD in Development Economics} --- Universit\'{e} Clermont Auvergne / LEO\\
  & Supervisors: Prof.\ J.-L.\ Combes \& Prof.\ P.\ Motel Combes;
    Collab.: Prof.\ J.-C.\ Kouladoum (N'Djam\'{e}na)\\[0.5pt]
2023--2025 &
  \textbf{Master 2 in Development Economics} --- Universit\'{e} Clermont Auvergne\\[0.5pt]
2022--2023 &
  \textbf{Aspire Leaders Program} --- Aspire Institute / Harvard University\\[0.5pt]
2018--2021 &
  \textbf{Licence in Economics} --- Kigali Independent University, Rwanda\\
\end{tabularx}
}

%% ---- EXPERIENCE -------------------------------------------
\cvsection{Professional Experience}
{\footnotesize
\begin{tabularx}{\linewidth}{@{} D X @{}}
Feb--Jul 2025 &
  \textbf{Intern, Strategic \& Impact Evaluation} ---
  ADE (Aide \`{a} la D\'{e}cision \'{E}conomique), Belgium\\
  & EU evaluations: EU--DRC (2021--24), Refugees in Turkey, GAP III;
    IATI extraction, QGIS, AI classification.\\[0.5pt]
Oct--Dec 2024 &
  \textbf{English Tutor} --- Universit\'{e} Clermont Auvergne\\[0.5pt]
2024 &
  \textbf{Deputy Coordinator} --- ATIMM Foundation\\[0.5pt]
2022 &
  \textbf{Public Policy Analyst Intern} ---
  Obs.\ National du Dividende D\'{e}mographique, Chad\\[0.5pt]
2021 &
  \textbf{Opinion Writer Intern} --- The Campus Ltd., Rwanda\\
\end{tabularx}
}

%% ---- RESEARCH ---------------------------------------------
\cvsection{Research (PhD Thesis)}
{\footnotesize
\begin{tabularx}{\linewidth}{@{} >{\color{mgray}\footnotesize}p{0.9cm} X @{}}
Ch.\,1 &
  \textit{IMF Programmes and Public Investment in the Global South.}
  Preliminary analysis; working paper in preparation.\\[0.5pt]
Ch.\,2 &
  \textit{Global Financial Cycles and Macroeconomic Sovereignty.}
  Data construction / preliminary design.\\[0.5pt]
Ch.\,3 &
  \textit{Resource Dependence, Fiscal Resilience, Structural Transformation.}
  Under development.\\[0.5pt]
Ch.\,4 &
  \textit{Hydropower and Forest Loss in Virunga (Matebe Project, DRC).}
  Working paper, preparing for journal submission.\\
\end{tabularx}
}

%% ---- SKILLS & LANGUAGES -----------------------------------
\cvsection{Methods, Tools \& Languages}
{\footnotesize
\textbf{Methods:} Panel data $\cdot$ event studies $\cdot$ local projections $\cdot$
  spatial DiD $\cdot$ DiD $\cdot$ PSM $\cdot$ synthetic control $\cdot$
  time series $\cdot$ geospatial analysis $\cdot$ remote sensing.\\[0.5pt]
\textbf{Software:} R $\cdot$ Stata $\cdot$ Python $\cdot$ QGIS $\cdot$
  Google Earth Engine $\cdot$ \LaTeX $\cdot$ Git/GitHub $\cdot$ Excel.\\[0.5pt]
\textbf{Languages:} French (fluent) $\cdot$ English (fluent) $\cdot$
  Arabic (fluent) $\cdot$ Spanish (basic).
}

\end{document}
